Gait Segmentation Model for Rotation Time Series Collected by a Wearable Sensor using Machine Learning

### 2025-01-27 article_segmentation.qmd
Add centering options to table 1.

```{r}
data.frame(
  id = c("MBA", "MBO", "MSI", "MTR", "NNE", "TDE"),
  gender = c("M", "F", "F", "M", "F", "M"),
  age = c("50-60", "20-30", "20-30", "20-30", "20-30", "50-60"),
  slow = c(60, 73, 67, 77, 57, 61),
  intermediate = c(116, 122, 115, NA, 116, NA),
  preferential = c(145, 145, 148, 132, 147, 120),
  fast = c(199, 188, 179, 185, 190, 193)
) |> 
  gt::gt() |> 
  gt::tab_spanner(
    label = "Walking speed (cm/s)",
    columns = c(slow, intermediate, preferential, fast)
  ) |> 
  gt::cols_label(
    id = "ID",
    gender = "Gender",
    age = "Age range (years)",
    slow = "Slow",
    intermediate = "Intermediate",
    preferential = "Preferential",
    fast = "Fast"
  ) |> 
  gt::sub_missing() |> 
  gt::opt_stylize(style = 6, color = 'gray') |> 
  gt::tab_options(
    column_lab
  )
```

>>>>

```{r}
data.frame(
  id = c("MBA", "MBO", "MSI", "MTR", "NNE", "TDE"),
  gender = c("M", "F", "F", "M", "F", "M"),
  age = c("50-60", "20-30", "20-30", "20-30", "20-30", "50-60"),
  slow = c(60, 73, 67, 77, 57, 61),
  intermediate = c(116, 122, 115, NA, 116, NA),
  preferential = c(145, 145, 148, 132, 147, 120),
  fast = c(199, 188, 179, 185, 190, 193)
) |> 
  gt::gt() |> 
  gt::tab_spanner(
    label = "Walking speed (cm/s)",
    columns = c(slow, intermediate, preferential, fast)
  ) |> 
  gt::cols_label(
    id = "ID",
    gender = "Gender",
    age = "Age range (years)",
    slow = "Slow",
    intermediate = "Intermediate",
    preferential = "Preferential",
    fast = "Fast"
  ) |> 
  gt::sub_missing() |> 
  gt::opt_stylize(style = 6, color = 'gray') |> 
  gt::cols_align(align = "center") |> 
  gt::tab_style(
    style = "vertical-align:top", 
    locations = gt::cells_column_labels()
  )
```
